%% Master CV - Pranay Kiran
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% moderncv loads hyperref itself, so a second \usepackage{hyperref} triggers
% "Option clash for package hyperref". Configure it with \hypersetup instead.
% Both the hyperref config and the blue name/section-heading overrides are
% deferred to \AtBeginDocument so they run after moderncv has defined its
% style hooks (a bare \renewcommand*{\firstnamestyle} in the preamble errors
% with "command undefined" on TeX Live). Default banking otherwise leaves the
% name and section headings black, inconsistent with the blue accent scheme.
\AtBeginDocument{%
  \hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=blue,%
    pdftitle={Pranay Kiran - CV},pdfpagemode=FullScreen}%
  % moderncv 2.3.x on TeX Live styles the whole name through \namestyle; some
  % MiKTeX builds instead expose \firstnamestyle/\lastnamestyle. \providecommand
  % first makes each hook exist (harmless identity where the build doesn't use
  % it), then \renewcommand paints it blue so the name matches the accent scheme.
  \providecommand*{\namestyle}[1]{#1}%
  \renewcommand*{\namestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}%
  \providecommand*{\firstnamestyle}[1]{#1}%
  \renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}%
  \providecommand*{\lastnamestyle}[1]{#1}%
  \renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}%
  \renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}%
}

% personal data
\name{Pranay}{Kiran}
\address{Hyderabad, Telangana, India}{}{}
\phone[mobile]{+91-9676504552}
\email{kiranpranay12@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/pranaykiran/}{LinkedIn}, \href{https://github.com/KiranPranay}{GitHub}, \href{https://pranay.cottonseeds.org}{Portfolio}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Mechanical design engineer specializing in defense and aerospace-grade lithium thermal batteries, with hands-on experience taking products from concept through CAD, simulation, and validated production. Combines strong CFD and FEA capability (thermal, structural, and fluid analysis) with practical design-for-manufacturability and MIL-STD qualification expertise. Currently pursuing an M.Tech in Aerospace Engineering to deepen domain knowledge alongside a full-time design and development role. Comfortable bridging design, manufacturing, and automation, with working proficiency in Python, MATLAB, and IoT-based process integration.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Mechanical Design \& CAD}: Siemens NX, SolidWorks, Fusion 360, AutoCAD, FreeCAD; tolerance stack-up, GD\&T.

\item \textbf{CFD \& FEA}: thermal, structural, fluid, vibration and fatigue analysis using ANSYS Fluent and OpenFOAM.

\item \textbf{Manufacturing \& DFM}: jigs, fixtures, test equipment, production-line setup, inert glovebox and argon systems.

\item \textbf{Standards \& Qualification}: MIL-STD-810H and MIL-STD-461G, environmental and qualification testing.

\item \textbf{Programming \& Automation}: Python, MATLAB, C++, Git, Linux; IoT and ESP32-based process integration.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\needspace{5\baselineskip}
\item{\cventry{2023--Present}{Design \& Development Engineer (Mechanical)}{Renewable Energy Systems Ltd}{Hyderabad, India}{}{\vspace{1pt}
\begin{itemize}
    \item Established a defense-grade lithium thermal battery manufacturing facility with inert gloveboxes, argon circulation, and controlled production processes compliant with MIL-STD-810H and MIL-STD-461G.
    \item Developed repeatable, validated CFD/FEA simulation strategies for thermal and structural performance of battery components, reducing prototype iterations by 30\% and improving design-verification accuracy.
    \item Digitized process parameters and production data to establish end-to-end design-to-production traceability, reducing manual effort and errors by 90\%.
    \item Designed production jigs, fixtures, and test equipment; performs CAD modeling, tolerance stack-up, and FEA for high-temperature structural components.
    \item Leads automation and IoT integration projects for inert glovebox and process systems to improve manufacturability.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\needspace{5\baselineskip}
\item{\cventry{2022}{Intern}{Bharat Heavy Electricals Limited (BHEL)}{Hyderabad, India}{}{\vspace{1pt}
\begin{itemize}
    \item Trained in manufacturing processes and quality control for steam-turbine production.
    \item Assisted in the design and analysis of turbine components using CAD and FEA tools.
\end{itemize}}}

\vspace{3pt}

% --- Earlier Role ---
\needspace{5\baselineskip}
\item{\cventry{2021--2023}{General Secretary}{Service to Mankind (NGO)}{Hyderabad, India}{}{\vspace{1pt}
\begin{itemize}
    \item Established and led NGO operations supporting underprivileged children through educational and healthcare initiatives, facilitating 300+ blood donations and multiple medical-assistance programs.
    \item Built the NGO's operational infrastructure: constitution, an open-source website, and an administrative dashboard with transparent donation tracking.
\end{itemize}}}

\end{itemize}

% ============================================================
%     SELECTED PROJECTS
% ============================================================

\section{Selected Projects}
\vspace{1pt}
\begin{itemize}

\item \textbf{Lithium Thermal Battery Manufacturing Line}: designed an end-to-end aerospace-compliant production line with gloveboxes, argon circulation, and robotic stations, with a repeatable validation methodology enabling in-house R\&D-to-production transition.

\item \textbf{Thermal-Insulation Simulation (OpenFOAM, C++, Gmsh, Python)}: transient thermal models of a lithium thermal battery under high-temperature, cold-soak, and ambient conditions, studying insulator material and thickness and correlating results with experimental testing.

\item \textbf{Robotic Arm \& Assembly Guidance System (ESP32, custom PCB, Python)}: IoT-based LED guidance and robotic sequencing for precision assembly, reducing operator dependency, eliminating assembly errors, and increasing throughput by 30\%.

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\needspace{3\baselineskip}
\item{\cventry{Expected 2026}{M.Tech in Aerospace Engineering}{Malla Reddy College of Engineering and Technology}{Hyderabad, India}{}{}}

\vspace{3pt}

\item{\cventry{2019--2023}{B.Tech in Mechanical Engineering}{MLR Institute of Technology}{Hyderabad, India}{}{}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (professional), Telugu (native), Hindi (professional).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
